\section{How to include lists}\label{sec7}

List in \LaTeX{} can be of three types: numbered, bulleted, and unnumbered. The ``enumerate'' environment produces a numbered list, the 
``itemize'' environment produces a bulleted list, and the ``unlist''
environment produces an unnumbered list.
In each environment, a new entry is added via the \verb+\item+ command.

\begin{enumerate}[label=\arabic*.]
\item This is the 1st item
\item Enumerate creates numbered lists, itemize creates bulleted lists, and unnumerate creates unnumbered lists.

\begin{enumerate}[label=\alph*.]
\item Second level numbered list. Enumerate creates numbered lists, itemize creates bulleted lists, and description creates unnumbered lists.
\item Second level numbered list. Enumerate creates numbered lists, itemize creates bulleted lists, and description creates unnumbered lists.

\begin{enumerate}[label=(\roman*)]
\item Third level numbered list. Enumerate creates numbered lists, itemize creates bulleted lists, and description creates unnumbered lists.
\item Third level numbered list. Enumerate creates numbered lists.
\end{enumerate}

\item Second level numbered list. Enumerate creates numbered lists, itemize creates bulleted lists, and description creates unnumbered lists.
\end{enumerate}

\item Numbered lists continue.
\end{enumerate}
Lists in \LaTeX{} can be of three types: enumerate, itemize, and description.
In each environment, a new entry is added via the \verb+\item+ command.

\begin{itemize}
\item First level bulleted list. This is the 1st item
\item First level bulleted list. Itemize creates bulleted lists, and description creates unnumbered lists.

\begin{itemize}
\item Second level dashed list. Itemize creates bulleted lists, and description creates unnumbered lists.
\item Second level dashed list. Itemize creates bulleted lists, and description creates unnumbered lists.
\end{itemize}

\item First level bulleted list. Bullet lists continue.
\end{itemize}

\noindent
Example of unnumbered list items:

\begin{unlist}
\item Sample unnumberd list text. Sample unnumberd list text. Sample unnumberd list text. Sample unnumberd list text. Sample unnumberd list text.

\item Sample unnumberd list text. Sample unnumberd list text. Sample unnumberd list text.

\item Sample unnumberd list text. Sample unnumberd list text. Sample unnumberd list text. Sample unnumberd list text. 
\end{unlist}


%--- Section ---%
